### 2022-09-27 README.Rmd
nhaneTrends no more
put table 1 in readme?

You can install the development version of nhanesTrends from [GitHub](https://github.com/) with:

@@

## Weights

@@

## Validation of results from the shiny application

@@

>>>>

You can install the development version of cardioStatsUSA from [GitHub](https://github.com/) with:

@@

## Why we made this

## Methods

### Weights

@@

### Validation of results from the shiny application

@@

## Results

### Participant characteristics

```{r}

suppressPackageStartupMessages({
 library(cardioStatsUSA)
 library(magrittr)
 library(gtsummary)
 library(tidyverse)
 library(survey)
 library(gt)
})

tbl_summary_data <- as_tibble(nhanes_bp) %>% 
 filter(svy_subpop_htn == 1) %>% 
 mutate(nobs = 1) %>% 
 select(
  svy_psu,
  svy_strata,
  svy_weight_mec,
  svy_year,
  nobs,
  starts_with('demo'),
  starts_with('bp'), - bp_cat_meds_excluded,
  starts_with('htn'),
  starts_with('cc')
 )

for(i in names(tbl_summary_data)){
 attr(tbl_summary_data[[i]], 'label') <- nhanes_key$variables[[i]]$label
}

tbl_summary_design <- tbl_summary_data %>% 
 svydesign(ids = ~ svy_psu,
           strata = ~ svy_strata,
           weights = ~ svy_weight_mec,
           data = .,
           nest = TRUE)

tbl_summary_design %>% 
 tbl_svysummary(
  by = svy_year,
  include = c(nobs, 
              starts_with("demo"),
              starts_with('bp'), 
              starts_with('htn'),
              starts_with('cc')),
  missing = 'no',
  label = list(nobs ~ "No. of Adults"),
  statistic = list(
   all_categorical() ~ "{p}",
   all_continuous() ~ "{mean} ({sd})",
   nobs ~ "{N_unweighted}"
  )
 ) %>%
 modify_header(all_stat_cols() ~ "**{level}**") %>%
 modify_footnote(all_stat_cols() ~ NA) %>%
 as_gt() %>%
 tab_source_note("Table values are mean (standard deviation) or percent.")
